---
title: "Feature selection and machine learning models"
output: html_document
---

```{r loadInformations, message = FALSE, warning = FALSE, echo = FALSE}
library(cowplot)
library(kableExtra)
library(caret)
library(MASS)
library(ROCR)
library(dplyr)
library(formattable)
source("functions.R")
dataPath                          <- file.path(getwd(), "data")
folderToSavePlots                 <- file.path(getwd(), "plots")
folderToSavecalculations          <- file.path(getwd(), "calculations")
folderToSavePlotsSelectedFeatures <- file.path(folderToSavePlots, "selectedFeatures")
folderToSavecalculations          <- file.path(folderToSavePlots, "..", "calculations")

load(file = file.path(folderToSavecalculations, "resultsOfIV_allvariables.Rdata"))
load(file = file.path(folderToSavecalculations, "iv_in_variable_bins_plots.Rdata"))
load(file = file.path(folderToSavecalculations, 'iVForSelectedcontinuousVariablesWithChoosenBins.Rdata'))
load(file = file.path(folderToSavecalculations, "listOfSeletedVariables.Rdata"))
load(file.path(folderToSavecalculations, "categorisationVariableParametrs.Rdata"))
load(file = file.path(dataPath, "dataNew.Rdata"))
load(file = file.path(dataPath, "dataTrainWithNewFeatures.Rdata"))
load(file = file.path(folderToSavecalculations, "own_choosen_variables_using_owe.Rdata")) ##dane do modelu logistycznego, gdzie sama wybralam bins do 
load(file = file.path(folderToSavecalculations, "plots_iv_in_time_for_choosen_variables.Rdata"))
load(file = file.path(folderToSavePlots, "listOfPlotsTimeSeries.Rdata"))
  variablesFromFeature        <<- c("sub_grade", "grade", "int_rate", "installment", "total_pymnt", "total_pymnt_inv", "total_rec_prncp", "total_rec_int", "total_rec_late_fee", "recoveries", "collection_recovery_fee", "last_pymnt_amnt", "initial_list_status")
  variablesAnotherToDelete    <<- c("id", "member_id", "issue_d", "loan_status", "funded_amnt_inv", "term", "verification_status", "funded_amnt", "group", "last_credit_pull_d", "collections_12_mths_ex_med", "acc_now_delinq")
  
groupedVariables <- c("quarter", "month")
variablesName <- names(dataTrainWithNewFeatures)[which(!names(dataTrainWithNewFeatures) %in% groupedVariables)]
continuous_variables <- listOfSeletedVariables$continuous
discrete_variables <- listOfSeletedVariables$discrete
dataTrainWithNewFeatures <- dataTrainWithNewFeatures[, which(!names(dataTrainWithNewFeatures) %in% c("quarter", "month"))]
```


## Model building

1. Logistic Regression
    
    + With weight of evidence coding variables
    
        + Feature selecion using Information value (IV) and weight of evidence (Woe)

IV values:        
```{r iv, message = FALSE, warning = FALSE, echo = FALSE}
cowplot::plot_grid(results$iv_for_all_variables_plot) 
rownames(results$information_table$Summary) <- c()

results$information_table$Summary %>%
  mutate(IV = round(IV, 5),
         `Is it a useful variable? ?` = IV)%>%
  formattable(list(`Is it a useful variable? ?` = formatter("span", x ~ icontext(ifelse(x >0.02, "ok", "remove"),
                                                                                        ifelse(x>0.02, "Yes", "No")),
                                                                   style = x ~ style(color = ifelse(x>0.02, "green", "red")))))


cowplot::plot_grid(plotlist =  plots_of_iv_and_bins)  


```

</br>
</br>

Woe values:

```{r woe, message = FALSE, warning = FALSE, echo = FALSE}

cowplot::plot_grid(plotlist =  results$plotsOfWoe[1:4])
cowplot::plot_grid(plotlist =  results$plotsOfWoe[5:8])
cowplot::plot_grid(plotlist =  results$plotsOfWoe[9:12])
cowplot::plot_grid(plotlist =  results$plotsOfWoe[13:16])
cowplot::plot_grid(plotlist =  results$plotsOfWoe[17:20])
cowplot::plot_grid(plotlist =  results$plotsOfWoe[21:23])
```



```{r dataWithWithWoe, message = FALSE, warning = FALSE, echo = FALSE }
dataSetWithVariablesCodedWoe <- assignWoeValueInVariables(variables_name = continuous_variables,
                                                          listOfWoe = informationTableSelectedVariables,
                                                          data = dataTrainWithNewFeatures)

dataSetWithVariablesCodedWoe[["home_ownership_woe"]] <- as.factor(
  with(dataTrainWithNewFeatures, dplyr::case_when(home_ownership == "MORTGAGE" ~ -0.19739742,
                                                  home_ownership == "OWN"  ~ 0.07469287,
                                                  home_ownership == "RENT" ~ 0.17447816)))

dataSetWithVariablesCodedWoe <- dataSetWithVariablesCodedWoe %>% dplyr::select(contains("_woe"))
dataSetWithVariablesCodedWoe[["target"]] <- dataTrainWithNewFeatures$target
dataSetWithVariablesCodedWoe <- dataSetWithVariablesCodedWoe %>%
  mutate_at(c("annual_inc_woe", "dti_woe", "tot_cur_bal_woe", "total_rev_hi_lim_woe", "revol_util_woe", "total_acc_woe", "home_ownership_woe"),
            funs(as.numeric(as.character(.))))

```

        + Feature selecion using Information value (IV) and weight of evidence (Woe)

```{r correlations, message = FALSE, warning = FALSE, echo = FALSE}

names_of_independent_variables_coded_woe <- names(dataSetWithVariablesCodedWoe)
names_of_independent_variables_coded_woe <- names_of_independent_variables_coded_woe[which(!names_of_independent_variables_coded_woe %in% c("target"))]

correlations_independent_variables_coded_woe <- round(cor(dataSetWithVariablesCodedWoe[, names_of_independent_variables_coded_woe]),3)
corrplot::corrplot(correlations_independent_variables_coded_woe)
colnames(correlations_independent_variables_coded_woe)[findCorrelation(correlations_independent_variables_coded_woe, cutoff = 0.6)]

correlations_independent_variables_coded_woe %>%
  as.data.frame() %>%
  formattable(list(area(col = 1:ncol(correlations_independent_variables_coded_woe)) ~ color_bar("orange")))

```

I created the full model with all the choosen independent variables (annual_inc_woe, dti_woe, tot_cur_bal_woe, total_rev_hi_lim_woe, revol_util_woe, total_acc_woe, home_ownership_woe)
Let’s name it model_lr_woe Summary of the model is as below:








