---
title: "Who are the borrowers ?"
output: md_document 
---

## *Let's get more information about the borrowers* 

&nbsp;

### **Word cloud of types of job titles**

To create Word Clouds is needed load these packages:

- *tm*,
- *wordcloud*,
- *RColorBrewer*,

&nbsp;

```{r setup, echo = FALSE, message=FALSE, warning=FALSE }
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("tidyverse")
library("data.table")
library("cowplot")
pathFunctions <- file.path(getwd(),"..", "code", "functions")
dataPath <- file.path(getwd(), "..", "data")
folderToSavePlots <- file.path(getwd(), "..", "plots")
source(file.path(pathFunctions, "functions.R"))
set.seed(1234)
```

From data LC (from 2013-01-01 to 2015-01-01) selected samples of variable `empl_title`. Created two samples of the dataset:

- the sample of borrowers who didn't pay off loan,
- the sample of borrowers who paid off.  

This dataset applies to customers who took out a loan for 36 months.
A stable number of target was selected in dataset (from 2013-01 to 2015-01).&nbsp;
These chart represents how the number of bad customers has changed over time.&nbsp; 
&nbsp; 

```{r timeSeriesPlot,  echo = FALSE, message = FALSE, warning = FALSE}
load(file = file.path(folderToSavePlots, "listOfPlotsTimeSeries.Rdata"))
cowplot::plot_grid(listOfPlotsTimeSeries$plotTargetInSelectedData)
```


```{r prepareData, echo = FALSE, message = FALSE, warning = FALSE}
data <- fread(file.path(dataPath, "loan.csv"))
data <- setDF(data)
data <- data %>% filter(term == "36 months") 
data <- data %>% mutate(funded_loan_date = convert_date_from_month_year(issue_d),
                        earliest_cr_line_date = convert_date_from_month_year(earliest_cr_line),
                        last_credit_pull_date = convert_date_from_month_year(last_credit_pull_d)) 

dataReduced <- data[which(data$funded_loan_date >= '2013-01-01' & data$funded_loan_date <= '2015-01-01'), ]
dataReduced$target <- case_when(dataReduced$loan_status == "Fully Paid"  ~ '0',
                                dataReduced$loan_status == "Charged Off" ~ '1',
                                dataReduced$loan_status == "Default Does not meet the credit policy. Status:Charged Off" ~ '1',
                                TRUE ~ as.character(dataReduced$loan_status))
  
dataReduced <- dataReduced[which(dataReduced$target %in% c("0", "1")), ]
dataReduced$target <- as.factor(dataReduced$target)
borrowersWithDefault <- dataReduced[which(dataReduced$target == 1), "emp_title"]
borrowersWithoutDefault <- dataReduced[which(dataReduced$target == 0), "emp_title"]  
borrowersWithoutDefault <- sample(x = borrowersWithoutDefault, size = 30000)  
purposesBorrowers <- dataReduced[, "purpose"]
purposesBorrowers <- sample(x = purposesBorrowers, size = 40000)  

```


The some examples of employment title from the dataset:
&nbsp;

```{r exampleOfEmps, echo = FALSE, message = FALSE, warning = FALSE}
head(borrowersWithDefault, 20)
```


### **Converting the text file into a Corpus**

It is needed to load the data as a [corpus](https://www.rdocumentation.org/packages/tm/versions/0.7-7/topics/Corpus)).

```{r corpus, echo = TRUE, message = FALSE, warning = FALSE }
docsBorrowersDefault        <- Corpus(VectorSource(borrowersWithDefault))
docsBorrowersWithoutDefault <- Corpus(VectorSource(borrowersWithoutDefault))
docspurposesBorrowers       <- Corpus(VectorSource(purposesBorrowers))
```


### **Text cleaning**

Used function `tm_map()` from the `tm` package for processing text (some operations on the text):

* strip unnecessary white space,  

* convert everything to lower case,

* remove numbers and punctuation with the removeNumbers and removePunctuation arguments.

```{r cleaningText, echo = TRUE, message = FALSE, warning = FALSE}
docsBorrowersDefault_tm <- tm_map(docsBorrowersDefault, stripWhitespace)
docsBorrowersDefault_tm <- tm_map(docsBorrowersDefault_tm, tolower)
docsBorrowersDefault_tm <- tm_map(docsBorrowersDefault_tm, removeNumbers)
docsBorrowersDefault_tm <- tm_map(docsBorrowersDefault_tm, removePunctuation)
docsBorrowersDefault_tm <- tm_map(docsBorrowersDefault_tm, removeWords, stopwords('english'))

docsBorrowersWithoutDefault_tm <- tm_map(docsBorrowersWithoutDefault, stripWhitespace)
docsBorrowersWithoutDefault_tm <- tm_map(docsBorrowersWithoutDefault_tm, tolower)
docsBorrowersWithoutDefault_tm <- tm_map(docsBorrowersWithoutDefault_tm, removeNumbers)
docsBorrowersWithoutDefault_tm <- tm_map(docsBorrowersWithoutDefault_tm, removePunctuation)
docsBorrowersWithoutDefault_tm <- tm_map(docsBorrowersWithoutDefault_tm, removeWords, stopwords('english'))

docspurposesBorrowers_tm <- tm_map(docspurposesBorrowers, stripWhitespace)
docspurposesBorrowers_tm <- tm_map(docspurposesBorrowers_tm, tolower)
docspurposesBorrowers_tm <- tm_map(docspurposesBorrowers_tm, removeNumbers)
docspurposesBorrowers_tm <- tm_map(docspurposesBorrowers_tm, removePunctuation)
docspurposesBorrowers_tm <- tm_map(docspurposesBorrowers_tm, removeWords, stopwords('english'))
```


### **Creating word clouds**

&nbsp;

#### Word cloud of types of job titles (borrowers who paid off)

```{r clouds1, echo = TRUE, message = FALSE, warning = FALSE}
wordcloud (docsBorrowersWithoutDefault_tm,
           scale=c(5,0.5),
           max.words=200,
           random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, 'Dark2'))
```

&nbsp;

#### Word cloud of types of job titles (borrowers who didn't pay off loan)

```{r clouds2, echo = TRUE, message = FALSE, warning = FALSE}
wordcloud (docsBorrowersDefault_tm,
           scale=c(5,0.5),
           max.words=200,
           random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, 'Dark2'))
```

&nbsp;
&nbsp;

#### Word cloud of credit purpose

```{r clouds_purpose, echo = TRUE, message = FALSE, warning = FALSE}

wordcloud(docspurposesBorrowers_tm,
           scale=c(5,0.5),
           max.words=200,
           random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, 'Dark2'))
```


## **Conclusions** 

Using in R programming package *tm* and the word cloud generator package
*wordcloud* help us to analyze texts and to quickly visualize the keywords as a word cloud. Word clouds add simplicity for reporting qualitative data. This is a really good communication tool - easy to understand.

